Merge our grid with NEFSC

### 2022-08-09 Scripts/nefsc_index_script.Rmd
Estimated grid area for Chris D.

>>>>

# Estimate area of gridcell

Would it be possible for you to send me a file with the area in hectares for each of the “index” grid areas in your fish distribution analysis?  You sent me kg/ha as one field in the dataset, so I’m hoping that you also have hectares for each index area, and that it’s easy to send.

```{r area_estimation}

library("tidyverse")

# Load coordinate grid
coords <- MyFunctions::my_path("D", extra_path = "Spatial", name = "inter_grid_df.csv", read = T, header = T)

# 1.2 Estimate gridcell area based on global variables (m^2)
# Degree ressolution for area estimation
# https://rdrr.io/github/stineb/rbeni/src/R/area.R
# https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
# https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl

r_earth <- 6371000 # NASA's volumetric mean radious https://nssdc.gsfc.nasa.gov/planetary/factsheet/earthfact.html
res_lon <- 0.3 # lon degree resolution
res_lat <- 0.3 # lat degree resolution

coords <- coords %>% 
  mutate(
    area = (4 * r_earth^2 * 0.5 * res_lon * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * res_lat * pi/180))/10000
  )

write_csv(coords, "corrds_area.csv")

```{r plot_test}

ggplot(coords) +
  geom_tile(
    aes(
      x = lon,
      y = lat,
      fill = area
    )
  ) +
  scale_fill_gradient(low = "yellow", high = "red", na.value = NA)
